Double Trouble: Understanding Sex Differences in Synthetic Lethal interactions in Human Cancers \\~\\ Summer Wrap Up

### 2023-08-07 aug08meeting_pres4/may30ccgmeeting.tex
updates

% Title page details: 
\title[BEAP Dec 2022]{Double Trouble: Understanding Sex Differences in Synthetic Lethal interactions in Human Cancers \\~\\ Project Updates} 
\author{Alexander Turco}
\date{July 18, 2023}
\logo{\includegraphics[height=0.5cm, width=3cm]{logo.png}}

@@

	% Outline frame - SLIDE 2
	%\begin{frame}{Overview}

		%\begin{center}
		%\begin{minipage}{6cm}

		 % 		\begin{block}{} \hyperlink{link1}{Background Information} \end{block}
		  %		\begin{block}{} The Game Design Process \end{block}
		  %		\begin{block}{} Collection of Student Feedback \end{block}
		  %		\begin{block}{} Results \end{block}
		  		%\begin{block}{} Conclusions \end{block}
		  %		\begin{block}{} Future Work \end{block}

		%\end{minipage}
		%\end{center}

	%\end{frame}

@@

	%Also called synthetic sick because it can lead to reduced cell viability as opposed to death
	\begin{frame}{Recall: The Combined Inactivation of Two Genes Can Lead to Synthetic Lethal Interactions}
		\label{link1}

		\begin{itemize}
			\item Synthetic lethal interactions describe the relationship between two genes whose coupled inactivation, but not their individual inactivation, causes cell death or reduces cell viability \newline

			\includegraphics[width=11cm, height=2.5cm]{slbasic.png}

			\item Inactivation: Preventing or disabling normal function of a gene (e.g mutation)
			\end{itemize}
			\centering
			\large \textbf{Synthetic = Combining}
			\footnotetext[2]{\tiny\cite{lee2018harnessing}}
	\end{frame}

	% SLIDE 4 - I do Not Know if I am including this slide
	% The Graphic for this slide is an  
	% Entropy, which is measured by Shannon's Entropy equation is a measure of compositional complexity which uses the proportion of residue(s)
	% in a subsequence to measure the compositional state of that subseequence - A lower variety of residues = lower entropy 
	%\begin{frame}{Shannon's Entropy - MAYBE }

	%		$H = -L\sum p_i log_2(p_i)$

	%\end{frame}

	%Slide 6
	% Poly(ADP-ribose) polymerases (PARPs) repair DNA SSBs through the BER pathway. PARP inhibitors, such as olaparib, prevent repair by trapping the inactivated PARP onto the SSB, resulting in the generation of DNA DSBs during the replication process. In tumors with a homologous recombination deficiency (HRD), such as a BRCA1/2 mutation, the low-fidelity repair mechanism of NHEJ leads to increasing genetic instability and ultimately death of the tumor cell.
	\begin{frame}{Recall: Synthetic Lethal Interactions are Harnessed for Precision Oncology}
		\begin{itemize} %(Olaparib, Niraparib, Rucaparib, Talazoparib)
			\item \small Four FDA approved anti-cancer drugs  are Poly [ADP-ribose] polymerase 1/2 (PARP1/2) inhibitors that work via a synthetic lethal mechanism

			\centering
			\includegraphics[width=8.5cm, height=6cm]{olaparib2.png}

			\footnotetext[4]{\tiny Figure From  \cite{o2015targeting}}
		\end{itemize}

	%EXPLAIN THE PROCESS OF ISLE HERE
	\begin{frame}{Recall: Building Pan-Cancer Synthetic Lethality Networks}
		\centering
		\includegraphics[width=13cm, height=7cm]{isle.png}
		%\movie[width=10cm,height=7cm,showcontrols=true]{\includegraphics[width=10cm, height=7cm]{pompe_thumbnail.png}}{pompe_trimmed.mp4}
		\footnotetext[2]{\tiny\cite{lee2018harnessing}}
	\end{frame}

	\begin{frame}{Recall: Sex Differences Add an Additional Layer of Complexity}
		Human sex differences are mainly caused by;
		\begin{enumerate}
			\item Gonadal hormone secretions
			\item Genes located on the sex chromosomes (X and Y) \newline
		\end{enumerate}
		This leads to differences in the frequency of certain cancer types and the efficacy of treatments in males and females
	\end{frame}

	\section{Approach}
	\begin{frame}{The Objective}
		\begin{center}
			%\includegraphics[width=11cm, height=6cm]{types_of_courses_taken.jpg}
			Can we build sex-specific synthetic lethality networks for various cancer types? \newline

			More specifically, we are trying to elucidate the differences in synthetic lethal interactions between males and females using a network based approach.
		\end{center}
	\end{frame}

@@

	\begin{frame}{Overall Project Workflow}
		\includegraphics[width=12cm, height=5.2cm]{img2.png}
	\end{frame}

>>>>

% Title page details: 
\title[BEAP Dec 2022]{Double Trouble: Understanding Sex Differences in Synthetic Lethal interactions in Human Cancers \\~\\ Summer Wrap Up} 
\author{Alexander Turco}
\date{August 8, 2023}
\logo{\includegraphics[height=0.5cm, width=3cm]{logo.png}}

@@

	% Outline frame - SLIDE 2
	\begin{frame}{Overview}

		\begin{center}
		\begin{minipage}{6cm}

		  		\begin{block}{} Overall Objective and Approach \end{block}
		  		\begin{block}{} Synthetic Lethality Analysis Update \end{block}
		  		\begin{block}{} Limitations of the Study \end{block}
		  		\begin{block}{} Next Steps/Future Work \end{block}
		  		\begin{block}{} Takeaways \& Tips for Future Undergrads \end{block}

		\end{minipage}
		\end{center}

@@

	\begin{frame}{Overall Objective}
		\begin{itemize}
			%\includegraphics[width=11cm, height=6cm]{types_of_courses_taken.jpg}
			\item Can we build sex-specific synthetic lethality networks for various cancer types? \newline

			\item More specifically, we are trying to elucidate the differences in synthetic lethal interactions between males and females using a network based approach.
		\end{itemize}
	\end{frame}

@@

	\section{Approach}
	\begin{frame}{Overall Project Workflow}
		\includegraphics[width=12cm, height=5.2cm]{img2.png}
	\end{frame}
